---
title: "Predicting Weight Lifting Quality Exercise"
author: "Toni Massó Jou"
date: "26/02/2016"
output: html_document
---

#Executive Summary
In this document to predict the manner in which people do some exercise. This is the "classe" variable in the training set. I use any of the other variables to predict with. The variables are data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. The classe variable is a factor of 5 levels: A,B,C,D,E.  Class A means that the exercise was doing well, on the other hand, B,C,D,E means that people was doing some common mistake.

#Loading libraries

I use doMC to work in parallel. My computer has 4 cores. 
```{r}
library(caret)
library(pgmm)
library(rpart)
library(gbm)
library(lubridate)
library(forecast)
library(e1071)
library(doMC)
registerDoMC(cores = 4)
```


#Loading Data

I load the data in two dataframes. One dataset is for training, the other is for testing. The testing dataset hsa only 20 test cases.

I recognize NA literals as NA in the dataframes.
```{r}
setwd("~/R/workspace/PracticalMachinLearning/Projecte")
training <- read.csv(file="Dades/pml-training.csv", header=TRUE, sep=",",na.strings=c('NA',''))
testing <- read.csv(file="Dades/pml-testing.csv", header=TRUE, sep=",",na.strings=c('NA',''))
```


#Exploratory Analysis and Cleaning Data

There are 19622 observations and 160 variables in the training dataset. 
 
```{r}
dim(training)
dim(testing)
```
Most of the variables are NA in all the observations, or have all NA in testing dataset. 
```{r}
apply(is.na(training), 2, all)
apply(is.na(testing), 2, all)

```


To clean data I drop all variables that have all the values as NA in training dataset and also in testing dataset.
```{r}
testing<-testing[, !apply(is.na(training), 2, all)]
training<-training[,!apply(is.na(training), 2, all)]
training<-training[,!apply(is.na(testing), 2, all)]
testing<-testing[, !apply(is.na(testing), 2, all)]
```
Now I have only 60 variables:

```{r}
dim(training)
dim(testing)
```


#Training Options and Cross Validation

I split the data training in a dataset for training, and another dataset to test the model. The proportion is 3/4. 

```{r}
inTrain = createDataPartition(training$classe, p = 3/4)[[1]]
validation = training[ inTrain,]
training = training[ inTrain,]
````
I use Repeated Cross Validation, with 3 repeats and 10 k-fold (default).

I think this option is the best to avoid overfiting. 

```{r}
ctrl <- trainControl(method = "repeatedcv",repeats = 3)
```

#Training models

I choose boosting. It's a very flexible model, and because I use repeted cross validation the overfitting would be low.


```{r}
modBoost<-train(classe~., data = training,method = 'gbm',trControl=ctrl)
valBoost<-predict(modBoost,validation)
confusionMatrix(valBoost,validation$classe)
```
 
The model sems very good. But being realistic the test dataset would have less accuracy. 
 

#Results of the Boosting model

```{r}
modBoost
```


#Predictions of the model


```{r}
predBoost<-predict(modBoost,testing)
predBoost
```

Predictor says all the observations in testing dataset would have classe A. Wich means that people of the testing dataset are doing well the exercise.




